Truthfulness Verification System

### 2011-04-13 trunk/proposal/paper.tex
Testing commit
added algorithm

{\em Mar 29 to Apr 12}
\begin{itemize}
\item Extraction of meaningful entities(noun phrase) in topic unit and dount unit by checking all combination of content words
\item Ranking 
\item Extracting 
\end{itemize}

@@

>>>>

{\em Mar 29 to Apr 12}
\begin{itemize}
\item Extraction of meaningful entities(noun phrase) in topic unit and dount unit by checking all combination of content words
\item Ranking based on finding content words in the interesction of two relevant wiki articles. 
\item Extracting 
\end{itemize}

@@

\section{Ranking Algorithm 2}
The main idea behind this ranking algorithm for alternative units is that Wikipedia should contain content words from doubt statement in the same sentence because of the similarity in the context. Details description of the algorithm is given below.

\begin{algorithm}
\small
\caption{Ranking Algorithm 2}
\label{alg:AssignScore} 
\begin{algorithmic}
\STATE Search google with topic unit
\STATE take first Wikipedia page from google search result
\STATE Extract all sentences from the Wikipedia page
\FOR{each alternate unit}
	\FOR{each sentence from Wikipedia page}
		\IF{alternate unit is found in the sentence}
			\IF{some content word found in the sentence}
				\STATE return true
			\ELSE
				\STATE return false	
			\ENDIF
		\ENDIF
	\ENDFOR
\ENDFOR		
\STATE assign same score to all true matches

\end{algorithmic}
\end{algorithm}
